A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-05 manuscript.Rmd
add citation for analytic procedure

At the heart of a PAC lies the planned analysis.
We suggest writing a function that captures the full process of testing a research question that receives a dataset as input.
For the hypothetical research question, we could for example plan to conduct a simple Student's t-test with Welch's correction an the average of machiavillism items between the gender groups.
As an example of data dependend decisions we included a rank transformation if the skewness greater than 1, converting the t-test to a supposedly more robust Mann–Whitney–Wilcoxon test.[^caution-mww]
This example is suboptimal with regard to several criteria (untested assumption of measurement invariance, underestimation of effectsize in presence of measurement error, overestimation of effectsize for highly skewed distributions), we merely choose it for didactic purposes because similar procedures a widely used (@horton reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005).

>>>>

At the heart of a PAC lies the planned analysis.
We suggest writing a function that captures the full process of testing a research question that receives a dataset as input.
For the hypothetical research question, we could for example plan to conduct a simple Student's t-test [@studentProbableErrorMean1908] with Welch's correction [@welchGeneralizationStudentProblem1947] an the average of machiavillism items of the Short Dard Triad (SD3) between the gender groups.
As an example of a data dependent decisions we included a rank transformation if the skewness greater than 1, converting the t-test to a supposedly more robust Mann–Whitney–Wilcoxon test.[^caution-mww]
This analyitical strategie is suboptimal with regard to several criteria (untested assumption of measurement invariance [@putnickMeasurementInvarianceConventions2016], underestimation of effect size in presence of measurement error [@frostCorrectingRegressionDilution2000], overestimation of effect size for highly skewed distributions[^caution-mww] [@stonehouseRobustnessTestsCombined1998]); we merely choose it for didactic purposes because similar procedures a widely used (@horton reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005).
